\section{Agreed Project Specification}
\label{sec:ProjBrief}

\textbf{Title:} Summarising Audiovisual Collections
\newline
\textbf{Supervisor:} Paul Lewis
\newline
\textbf{Team Members:} Michael Harris, Jonathan Harrison, Sami Kanza, Jenny Lantair
\newline
\textbf{Customer:} Matthew Addis at IT Innovation

\textbf{Project Specification:}

\textbf{Background}
\newline
The BBC has an audio visual archive, stretching back 50 years, which stores media broadcasted by the BBC for the purpose of preserving content and for compliance reasons. This archive is currently catalogued by hand which is very time consuming, for example it takes 10 hours to process 1 hour of material.

\textbf{Problem}
\newline
The problem is that there is limited metadata attached to this media therefore searching and summarising their content is extremely difficult. We have been given the task of producing Audio/Visual summaries of a collection; whereby a AV summary is a complete subset of a collection which represents the key elements of its content. Ideally, the AV summaries produced will be defined by a user’s metrics. These summaries could then be used applications such as Archive Monetisation, Rights Assessment and Archive Content Selection.

\textbf{Goals and Deliverables}

The goals of this project are:
\begin{itemize}
	\item{To build a AV summary of a collection using metrics such as:}
	\begin{itemize}
		\item{Main characters.}
		\item{Non key / guest characters.}
		\item{Key scenes.}
	\end{itemize}
	\item{To support AV data in MPEG2 format and DVB subtitle data in W3C Timed Text Markup Language.}
	 \item{To be able to process material faster than the current method of cataloging.}
	\item{If possible, construct a modular system to allow integration into existing Open Source tools.}
\end{itemize}
The deliverables of this project are: 
\begin{itemize}
	\item{A summarisation engine with a basic interface which allows users to produce an AV summary of a collection based on their parameters. }
\end{itemize}

